Standalone Tactics using OpenTheory

### 2012-05-12 paper.tex
tweak some "requirements of/for/on"

There are two approaches to obtaining a standalone tactic: either write one directly; or extract an existing tactic from an interactive theorem prover.
We have experimented with the second approach, extracting tactics from HOL4 and from HOL Light.
The procedure is reasonably lightweight, but less flexible than writing a standalone tactic directly.
For tactic extraction to succeed, the key requirements for the interactive theorem prover are:
\begin{enumerate}
\item\label{req:io} Ability to read and write \OpenTheory article files.

@@

Just as the requirements of an interactive theorem prover to use standalone tactics also enable it to import \OpenTheory packages in general, the first two requirements to create standalone tactics also enable a system to create and export \OpenTheory packages.
(The last requirement enables running on a server.)

>>>>

There are two approaches to obtaining a standalone tactic: either write one directly; or extract an existing tactic from an interactive theorem prover.
We have experimented with the second approach, extracting tactics from HOL4 and from HOL Light.
The procedure is reasonably lightweight, but less flexible than writing a standalone tactic directly.
For tactic extraction to succeed, the key requirements on the interactive theorem prover are:
\begin{enumerate}
\item\label{req:io} Ability to read and write \OpenTheory article files.

@@

Just as the requirements for an interactive theorem prover to use standalone tactics also enable it to import \OpenTheory packages in general, the first two requirements to create standalone tactics also enable a system to create and export \OpenTheory packages.
(The last requirement enables running on a server.)
